---
title: "LACN General Report"
output: 
  html_document:
    css: "style.css"
    theme: flatly
    toc: true
    toc_float: true
    toc_depth: 3
params:
  college: college
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE)

# load packages
library(tidyverse)
library(plyr)

# load LACN analysis environment
load("../lacn.RData")
```

#### 2020-21 Operations Survey {#subtitle}

<hr/>


## Introduction


### Enrollment

<div class="row">

  <div class="col-sm-7">

```{r enroll-plot}
enrollPlot() 
```

  </div>

  <div class="col-sm-5">

```{r enroll-table}
tableViz(enroll_data, var = "enroll")
```

  </div>

</div>


### Endowment

<div class="row">

  <div class="col-sm-7">

```{r endow-plot}
endowPlot() 
```

  </div>

  <div class="col-sm-5">

```{r endow-table}
tableViz(endow_data, var = "endow")
```

  </div>

</div>

<hr/>


## Reporting and Staffing

<div class="row">

  <div class="col-sm-7">

### Reporting Structure

```{r reporting-plot}
plot(cars)
```

  </div>


  <div class="col-sm-5">

```{r reporting-table}
plot(cars)
```

  </div>

</div>

### Steps Removed from President's Office

<div class="row">

  <div class="col-sm-7">

```{r steps-plot}
plot(cars)
```

  </div>

<div class="col-sm-5">

```{r steps-table}
plot(cars)
```

  </div>

</div>

### Student Staff (total)

<div class="row">

  <div class="col-sm-7">

```{r student-staff-plot}

suppressMessages(
  matrixViz("Q6", params$college)
)

```

  </div>


  <div class="col-sm-5">

```{r student-staff-table}

suppressMessages(
  matrixViz("Q6", params$college)
)

```

  </div>

</div>

### Professional (FTE)

<div class="row">

  <div class="col-sm-7">

```{r prof-plot}
plot(cars)
```

  </div>
  
  <div class="col-sm-5">

```{r prof-table}
plot(cars)
```
  
  </div>
  
</div>

### Student to Professional Staff (FTE) Ratio

<div class="row">

  <div class="col-sm-7">

```{r sp-ratio-plot}
plot(cars)
```

  </div>
  
  <div class="col-sm-5">

```{r sp-ratio-table}
plot(cars)
```

  </div>
  
</div>

### Professional Staff: Advising

<div class="row">

  <div class="col-sm-7">

```{r prof-advising-plot}
plot(cars)
```

  </div>
  
  <div class="col-sm-5">

```{r prof-advising-table}
plot(cars)
```
  
  </div>

</div>

### Professional Staff: Employer Relations

<div class="row">

  <div class="col-sm-7">

```{r prof-employer-plot}
plot(cars)
```

  </div>
  
  <div class="col-sm-5">

```{r prof-employer-table}
plot(cars)
```

  </div>
  
</div>

<hr/>


## Student/Alum Engagement

### Student Engagement by Class Year

<div class="row">

  <div class="col-sm-7">

```{r sengage-year-plot}
plot(cars)
```

  </div>
  
  <div class="col-sm-5">

```{r sengage-year-table}
plot(cars)
```

  </div>
  
</div>

### Student Engagement by Type of Engagement

<div class="row">

  <div class="col-sm-7">

```{r sengage-type-plot}
plot(cars)
```

  </div>
  
  <div class="col-sm-5">

```{r sengage-type-table}
plot(cars)
```

  </div>
  
</div>

### Professional Staff Appt w/ Students (by class year) (distribution)

<div class="row">

  <div class="col-sm-7">

```{r appt-student-dist-plot}
plot(cars)
```

  </div>
  
  <div class="col-sm-5">

```{r appt-student-dist-table}
plot(cars)
```

  </div>
  
</div>

### Professional Staff Appt w/ Students (by class year) (grouped bar)

<div class="row">

  <div class="col-sm-7">

```{r appt-student-group-plot}
plot(cars)
```

  </div>
  
  <div class="col-sm-5">

```{r appt-student-group-table}
plot(cars)
```

  </div>
  
</div>

### Professional Staff Appt w/ Alum

<div class="row">

  <div class="col-sm-7">

```{r appt-alum-plot}
plot(cars)
```

  </div>
  
  <div class="col-sm-5">

```{r appt-alum-table}
plot(cars)
```

  </div>
  
</div>

### Professional Staff Appt (+ email) per Total FTE

<div class="row">

  <div class="col-sm-7">

```{r appt-fte-plot}
plot(cars)
```

  </div>
  
  <div class="col-sm-5">

```{r appt-fte-table}
plot(cars)
```

  </div>
  
</div>

### Experiential Learning Participation

<div class="row">

  <div class="col-sm-7">

```{r exper-learning-plot}
plot(cars)
```

  </div>
  
  <div class="col-sm-5">

```{r exper-learning-table}
plot(cars)
```

  </div>
  
</div>

<hr/>

## Budget

### Total Available Funding

<div class="row">

  <div class="col-sm-7">

```{r total-funding-plot}
plot(cars)
```

  </div>
  
  <div class="col-sm-5">

```{r total-funding-table}
plot(cars)
```

  </div>
  
</div>

### Endowed Funds

<div class="row">

  <div class="col-sm-7">

```{r endow-fund-plot}
plot(cars)
```

  </div>
  
  <div class="col-sm-5">

```{r endow-fund-table}
plot(cars)
```

  </div>
  
</div>

### Expendable Gifts

<div class="row">

  <div class="col-sm-7">

```{r expend-gift-plot}
plot(cars)
```

  </div>
  
  <div class="col-sm-5">

```{r expend-gift-table}
plot(cars)
```

  </div>
  
</div>

<hr/>


Special thanks to **ACKNOWLEDGEMENTS HERE**


