---
title: "LACN General Report"
output: 
  html_document:
    css: "style.css"
    theme: flatly
params:
  college: college
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE)

# load packages
library(tidyverse)
library(plyr)

# load LACN analysis environment
load("../lacn.RData")
```

#### 2020-21 Operations Survey {#subtitle}

<hr/>

# {.tabset .tabset-pills}

<div class="row">
## Introduction
</div>

### Enrollment

<div class="row">

  <div class="col-sm-7">

```{r enroll-plot}
enroll_viz 
```

  </div>

  <div class="col-sm-5">

```{r enroll-table}
enroll_table
```

  </div>

</div>


### Endowment

<div class="row">

<div class="col-sm-7">

```{r endow-plot}
endow_viz 
```

</div>

<div class="col-sm-5">

```{r endow-table}
endow_table
```

</div>

</div>

<hr/>

## Reporting and Staffing

### Reporting Structure

```{r reporting-struc}
plot(cars)
```


### Steps Removed from President's Office

```{r steps-removed}
plot(cars)
```


### Student Staff (total)

```{r student-staff-total}

suppressMessages(
  matrixViz("Q6", params$college)
)

```

### Professional (FTE)

```{r prof-fte}
plot(cars)
```


### Student to Professional Staff (FTE) Ratio

```{r student-prof-ratio}
plot(cars)
```


### Professional Staff: Advising

```{r prof-advising}
plot(cars)
```


### Professional Staff: Employer Relations

```{r prof-employer}
plot(cars)
```



## Student/Alum Engagement

### Student Engagement by Class Year

```{r student-engage-year}
plot(cars)
```


### Student Engagement by Type of Engagement

```{r student-engage-type}
plot(cars)
```


### Professional Staff Appt w/ Students (by class year) (distribution)

```{r prof-appt-student-dist}
plot(cars)
```


### Professional Staff Appt w/ Students (by class year) (grouped bar)

```{r prof-appt-student-group}
plot(cars)
```

### Professional Staff Appt w/ Alum

```{r prof-appt-alum}
plot(cars)
```


### Professional Staff Appt (+ email) per Total FTE

```{r prof-appt-fte}
plot(cars)
```


### Experiential Learning Participation

```{r exper-learning}
plot(cars)
```



## Budget

### Total Available Funding

```{r total-funding}
plot(cars)
```


### Endowed Funds

```{r endow-fund}
plot(cars)
```


### Expendable Gifts

```{r expend-gift}
plot(cars)
```




