---
title: "Custom Report Test"
output: 
  html_document:
    css: "style.css"
    theme: flatly
    toc: true
    toc_depth: 3
    toc_float:
      collapsed: false
params:
  college: college
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE)

# load packages
library(tidyverse)
library(plyr)

# load LACN analysis environment
load("../lacn.RData")
```

##### LACN Operations Survey (2020-21) {#subtitle}
## Survey Results 

#{.tabset .tabset-fade .tabset-pills}

### Introduction

#### Undergraduate Enrollment

```{r undergrad-enroll}
plot(cars)
```

<hr/>

#### Endowment

```{r endowment}
plot(cars)
```



### Reporting and Staffing

#### Reporting Structure

```{r reporting-struc}
plot(cars)
```


#### Steps Removed from President's Office

```{r steps-removed}
plot(cars)
```


#### Student Staff (total)

```{r student-staff-total}

suppressMessages(
  matrixViz("Q6", params$college)
)

```

#### Professional (FTE)

```{r prof-fte}
plot(cars)
```


#### Student to Professional Staff (FTE) Ratio

```{r student-prof-ratio}
plot(cars)
```


#### Professional Staff: Advising

```{r prof-advising}
plot(cars)
```


#### Professional Staff: Employer Relations

```{r prof-employer}
plot(cars)
```



### Student/Alum Engagement

#### Student Engagement by Class Year

```{r student-engage-year}
plot(cars)
```


#### Student Engagement by Type of Engagement

```{r student-engage-type}
plot(cars)
```


#### Professional Staff Appt w/ Students (by class year) (distribution)

```{r prof-appt-student-dist}
plot(cars)
```


#### Professional Staff Appt w/ Students (by class year) (grouped bar)

```{r prof-appt-student-group}
plot(cars)
```

#### Professional Staff Appt w/ Alum

```{r prof-appt-alum}
plot(cars)
```


#### Professional Staff Appt (+ email) per Total FTE

```{r prof-appt-fte}
plot(cars)
```


#### Experiential Learning Participation

```{r exper-learning}
plot(cars)
```



### Budget

#### Total Available Funding

```{r total-funding}
plot(cars)
```


#### Endowed Funds

```{r endow-fund}
plot(cars)
```


#### Expendable Gifts

```{r expend-gift}
plot(cars)
```




