---
title: "General Report"
output: 
  html_document:
    css: "style.css"
    theme: flatly
    toc: true
    toc_float: true
    toc_depth: 3
params:
  plotfont: "Source Sans Pro"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

# load packages
library(tidyverse)
library(showtext)
library(sysfonts)

# load fonts
font_add_google(params$plotfont)

showtext_auto()

# load LACN analysis environment
load("../lacn.RData")
```

#### 2020-21 LACN Operations Survey {#subtitle}

<hr/>


## Introduction


### Undergraduate Enrollment

<div class="row">

  <div class="col-sm-7">

```{r enroll-plot}
enroll_data |>
  ggplot(mapping = aes(reorder(`Institution Name`,enroll), enroll))+
  geom_hline(yintercept = c(0,1000,2000,3000,4000), 
             colour = 'grey')+
  geom_bar(stat="identity", fill = "#7CBCE8")+
  
  labs(
    title = NULL,
    x = NULL,
    y = "Total"
  )+
  
  theme(
    axis.text.x = element_blank(),
    axis.ticks = element_blank(),
    panel.background = element_blank(),
    plot.margin = unit(c(1,1,1,1), "cm"),
    text = element_text(size = 45, family = params$plotfont)
  )
```

  </div>

  <div class="col-sm-5">

```{r enroll-table}
tableViz(enroll_data, var = "enroll")
```

  </div>

</div>


### Endowment

<div class="row">

  <div class="col-sm-7">

```{r endow-plot}

endow_data |>
  ggplot(mapping = aes(reorder(`Institution Name`,endow_bil), endow_bil))+
  geom_hline(yintercept = c(0,1,2,3), colour = "grey")+
  geom_bar(stat="identity", fill = "#7CBCE8")+
  
  scale_y_continuous(labels = c('0','1','2','$3'))+
  
   labs(
     title = NULL,
     x = NULL,
     y = "Total (in billions)"
   )+ 

  theme(
    axis.text.x = element_blank(),
    axis.ticks = element_blank(),
    panel.background = element_blank(),
    text = element_text(size = 45, family = params$plotfont)
  )
```

  </div>

  <div class="col-sm-5">

```{r endow-table}
tableViz(endow_data, var = "endow")
```

  </div>

</div>

<hr/>


## Reporting and Staffing

<div class="row">

### Reporting Structure

  <div class="col-sm-9">

```{r reporting-plot}

singlePlot(reporting_data, q = "Q2",
           string_rem = ":",
           size = 45,
           font = params$plotfont)

```

  </div>


  <div class="col-sm-3">

`r nTab(question_list$Q2['Institution Name'])`

  </div>

</div>

<div class="row">

### Steps Removed from President's Office

  <div class="col-sm-9">

```{r steps-plot}

  singlePlot(steps_data, q = "Q3",
           string_rem = "[:blank:]\\(.+\\)",
           size = 45,
           font = params$plotfont)

```

  </div>

<div class="col-sm-3">

`r nTab(question_list$Q3['Institution Name'])`

  </div>

</div>

### Advisory Boards

```{r advisory-boards}
all_list$multi$Q4 |>
  
  dplyr::filter(n>1) |>
  
  arrange(-n) |>
  
  mutate(freq = round(freq*100,2)) |>
  
  mutate(value = stringr::str_replace(value, "^My career.+boards$","No Advisory Boards"),
         value = stringr::str_replace(value, "^We report.+reps$","Academic Programs & Standards Committee")) |>
  
  serviceTab(q = "Q4", title = "Advisory Boards",
             subtitle = "",
             offer = "To Whom Do You Report?")
```

### Performance Metrics

*Relative Importance to Senior Leadership (N = 38)*

```{r performance-rank, fig.width = 9}
rank_data |>
  
  dplyr::filter(dim1 != "Other") |>
  ggplot(aes(reorder(dim1,-ranking_avg), ranking, colour = ranking))+
  geom_vline(xintercept = rank_data$dim1, colour = "grey")+
  geom_jitter(alpha = 0.5, width = 0, size = 3)+
  geom_point(aes(reorder(dim1,-ranking_avg), ranking_avg), 
             colour = "black",
             size = 3,
             shape = 21)+
  coord_flip()+
  scale_y_reverse(breaks = seq(1,11))+
  scale_color_gradientn(colours = c('#F7BF66','grey','#6AD4BF'))+
  scale_shape_identity()+
  
  labs(
    y = "Importance Ranking (1=highest)"
  )+
  
  annotate("text", 
           x = 9.5, 
           y = 5, 
           label = "Mean",
           colour = "black",
           size = 10)+
  
  annotate("segment", 
           x = 9,
           xend = 9.5, 
           y = deframe(rank_data[rank_data$dim1=="Diverse student engagement",'ranking_avg'][1,]), 
           yend = 4.5, 
           colour = "black")+
  
  theme(
    panel.background = element_blank(),
    text = element_text(family = params$plotfont, size = 40),
    axis.ticks.y = element_blank(),
    axis.title.y = element_blank(),
    axis.title.x = element_text(size = 25),
    legend.position = "none"
  )

```


### Student Staff (Total)

<div class="row">

  <div class="col-sm-7">

```{r student-staff-plot}

matrixPlot(student_staff_data, breaks = c(0,25,50,75,100),
           font = params$plotfont,
           size = 45)

```

  </div>


  <div class="col-sm-5">

```{r student-staff-table}

tableViz(data = student_staff_data,'n')

```

  </div>

</div>

### Student Staff (paraprofessional)

<div class="row">

  <div class="col-sm-7">

```{r student-para-plot}

matrixPlot(student_para_data, breaks = c(0,25,50,75,100),
           font = params$plotfont,
           size = 45)

```

  </div>


  <div class="col-sm-5">

```{r student-para-table}

tableViz(data = student_para_data,'n')

```

  </div>

</div>

### Student to Student Staff Ratio

<div class="row">

  <div class="col-sm-7">

```{r ss-ratio-plot}

matrixPlot(student_stustaff_ratio, breaks = c(0,250,500,750,1000),
           font = params$plotfont,
           size = 45)

```

  </div>
  
  <div class="col-sm-5">

```{r ss-ratio-table}

tableViz(student_stustaff_ratio, var='n')

```

  </div>
  
</div>



### Professional (Total FTE)

<div class="row">

  <div class="col-sm-7">

```{r prof-plot}
matrixPlot(prof_staff_data, breaks = c(0,10,20,30),
           font = params$plotfont,
           size = 45)
```

  </div>
  
  <div class="col-sm-5">

```{r prof-table}
tableViz(prof_staff_data, var = 'n')
```
  
  </div>
  
</div>

### Student to Professional Staff (FTE) Ratio

<div class="row">

  <div class="col-sm-7">

```{r sp-ratio-plot}

matrixPlot(student_prof_ratio, breaks = c(0,100,200,300,400,500),
           font = params$plotfont,
           size = 45)

```

  </div>
  
  <div class="col-sm-5">

```{r sp-ratio-table}

tableViz(student_prof_ratio, var='n')

```

  </div>
  
</div>

### Professional Staff: Advising

*(# who devote any level of time)*

<div class="row">

  <div class="col-sm-7">

```{r prof-advising-plot}
matrixPlot(prof_advising_data, breaks = c(0,10,20,30,40), 
           font = params$plotfont,
           size = 45)
```

  </div>
  
  <div class="col-sm-5">

```{r prof-advising-table}
tableViz(prof_advising_data, 'n')
```
  
  </div>

</div>

### Professional Staff: Employer Relations

*(# who devote any level of time)*

<div class="row">

  <div class="col-sm-7">

```{r prof-employer-plot}
matrixPlot(prof_employer_data,
           breaks = c(0,5,10,15), 
           font = params$plotfont, 
           size = 45)
```

  </div>
  
  <div class="col-sm-5">

```{r prof-employer-table}
tableViz(prof_employer_data, 'n')
```

  </div>
  
</div>

### National/Regional Conferences and Workshops

```{r conferences}

write_in_con <- question_list$Q9$Q9_11_TEXT

all_list$multi$Q9 |>
  
    add_row(value = "Career Leadership Collective ",
          n = 6,
          freq = 6/39) |>
  
  dplyr::filter(!is.element(value,write_in_con)) |>
  
  dplyr::mutate(freq = round(freq*100,2),
                value = str_remove(value,":")
                ) |>
  
  arrange(-n) |>
  
  serviceTab(q = "Q9", 
             title = "Conferences Attended by Staff",
             subtitle = "",
             offer = "Conferences")
```


<hr/>

## Services and Programs

### Services Offered: Undergraduate Students

```{r service-undergrad}

write_in_userve <- question_list$Q10$Q10_13_TEXT

all_list$multi$Q10 |>
  
  dplyr::filter(
    !is.element(value,write_in_userve)
  ) |>
  
  dplyr::mutate(
    value = dplyr::case_when(
      value == "Other:" ~ "Other",
      value == "Student on-campus employment" ~ "Student on-campus employment (managed)",
      TRUE ~ as.character(value)
    ),
    freq = round(freq*100,2), .keep = "unused"
  ) |>
  dplyr::arrange(-n)|>
  
  serviceTab(q = "Q10", title = "Services Offered to Undergraduates",
             subtitle = "",
             offer = "Services")

```

### Programs Offered: Undergraduate Students
```{r program-undergrad}
write_in_uprogram <- question_list$Q11$Q11_29_TEXT

all_list$multi$Q11 |>
  
  dplyr::filter(
    !is.element(value,write_in_uprogram)
  ) |>
  
  dplyr::mutate(
    value = dplyr::case_when(
      value == "Other:" ~ "Other",
      TRUE ~ as.character(value)
    ),
    freq = round(freq*100,2), .keep = "unused"
  ) |>
  dplyr::arrange(-n)|>
  
  serviceTab(
    q = "Q11",
    title = "Programs Offered to Undergraduates",
    subtitle = "",
    offer = "Programs"
  )
```




### Services Offered: Graduate Students

<div class="row">

  <div class="col-sm-7">
```{r service-grad-tab}

write_in_gserve <- question_list$Q13$Q13_4_TEXT

q13_n <- question_list[['Q13']] |>
  
  dplyr::filter(dplyr::if_any(.cols = !(1:2), .fns = ~ !is.na(.x))) |>
  
  nrow()

all_list$multi$Q13 |>
  
  mutate(value = stringr::str_to_title(value),
         freq = n/q13_n,
         freq = round(freq*100,2)) |>
  
  dplyr::arrange(-n) |>
  
  serviceTab(
    q = "Q13",
    title = "Services Offered to Grad Students",
    subtitle = "",
    offer = "Services"
  )
```
  </div>
  
  <div class="col-sm-5">
  
```{r service-grad-plot}
all_list$single$Q12 |>
  
  mutate(
    Q12 = replace_na(Q12, 'No Response')
  ) |>
  
  ggplot(aes(factor(Q12, levels=c('No','Yes','No Response')), 
             n, 
             fill = Q12, 
             label = n))+
  
  geom_hline(yintercept = seq(0,25,by=5), colour = "grey")+
  geom_bar(stat = "identity", width = 0.4)+
  geom_text(size = 20, colour = "white", nudge_y = -2)+
  
  scale_y_continuous(labels = seq(0,25,by=5))+
  scale_fill_manual(
    values = c('#F7BF66','#76828E','#6AD4BF')
  )+
  
  labs(
    title = "Offered Grad Services?",
    x = NULL,
    y = NULL
  )+
  
  theme(
    text = element_text(family = params$plotfont, size = 45),
    panel.background = element_blank(),
    axis.ticks = element_blank(),
    axis.text = element_text(size = 35, colour = "black"),
    legend.position = "none"
  )
```
  

  </div>
  
</div>

### Services Offered: Alumni
<div class="row">

  <div class="col-sm-7">
```{r service-alum}

q15_n <- question_list[['Q15']] |>
  
  dplyr::filter(dplyr::if_any(.cols = !(1:2), .fns = ~ !is.na(.x))) |>
  
  nrow()

all_list$multi$Q15 |>
  
  mutate(value = stringr::str_to_title(value),
         freq = n/q15_n,
         freq = round(freq*100,2)) |>
  
  dplyr::arrange(-n) |>
  
  serviceTab(q = "Q15", title = "Services Offered to Alumni",
             subtitle = "No write-in responses",
             offer = "Services")

```
  </div>
  
  <div class="col-sm-5">
  
  All institutions offer alumni services (`r nTab(question_list$Q15$Q15)`)

  </div>
  
</div>

<hr/>


## Employer Relations

### Info Sessions: Number Offered

<div class="row">

  <div class="col-sm-7">

```{r info-no-plot}
  
info_no_data |>  
  ggplot(aes(reorder(`Institution Name`,amount),amount))+
  
  geom_hline(yintercept = c(0,50,100,150,200), colour= "grey")+
  geom_bar(stat = "identity", fill = "#7CBCE8")+
  
  labs(
    y = "Total",
    x = NULL,
    fill = NULL
  )+
  
  theme(
    text = element_text(family = params$plotfont, size = 40),
    panel.background = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks = element_blank(),
    legend.position = "top"
  )
```
  </div>
  
  <div class="col-sm-5">
```{r info-no-table}
info_no_data |>
  group_by(`Institution Name`) |>
  summarise(amount = sum(amount)) |>
  tableViz(var = 'amount',
           subtitle = "All Sessions Virtual")
```
  
  </div>

</div>

### Info Sessions: Number of Employers

<div class="row">

  <div class="col-sm-7">

```{r info-employ-plot}
info_employ_data |>  
  ggplot(aes(reorder(`Institution Name`,amount),amount))+
  
  geom_hline(yintercept = c(0,50,100,150,200), colour= "grey")+
  geom_bar(stat = "identity", fill="#7CBCE8")+

  
  labs(
    y = "Total",
    x = NULL,
    fill = NULL
  )+
  
  theme(
    text = element_text(family = params$plotfont, size = 40),
    panel.background = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks = element_blank(),
    legend.position = "top"
  )
```
  </div>
  
  <div class="col-sm-5">
```{r info-employ-table}
info_employ_data |>
  group_by(`Institution Name`) |>
  summarise(amount = sum(amount)) |>
  tableViz(var = 'amount',
           subtitle = "All Sessions Virtual")
```
  
  </div>

</div>


<hr/>


## Student and Alumni Engagement

### Professional Staff Appointments with Students

a) Individual Schools by Class Year
b) Overall Metrics by Class Year

<div class="row">

  <div class="col-sm-9">

```{r appt-student-dist-plot}
appt_student_data |>
  
  ggplot2::ggplot(ggplot2::aes(reorder(`Institution Name`, Appt) ,Appt))+
  ggplot2::geom_hline(yintercept = c(0,2000,4000,6000), colour = "grey")+
  ggplot2::geom_bar(ggplot2::aes(fill = Year),
                    position = "stack",
                    stat = "identity") +

  ggplot2::scale_y_continuous(breaks = c(0,2000,4000,6000)) +
  ggplot2::scale_fill_manual(
    values=c(`First-Year` = "#76828E",
             Sophomore = "grey",
             Junior = "#6AD4BF",
             Senior = "#F7BF66"))+
  
  ggplot2::labs(
    y = "Total",
    x = NULL)+
  
   annotate("text",
           x = 5,
           y = 5000,
           label = "a)",
           size = 15,
           family = params$plotfont)+

  ggplot2::theme(
    text = ggplot2::element_text(size = 45, 
                                 family = params$plotfont),
    axis.text.x = ggplot2::element_blank(),
    axis.ticks = ggplot2::element_blank(),
    panel.background = ggplot2::element_blank(),
    legend.title = ggplot2::element_blank(),
    legend.text = ggplot2::element_text(size = 30, colour = "black"),
    legend.position = "right"
    )

```

  </div>
  
  <div class="col-sm-3">

```{r appt-student-dist-table}


tableViz(
  data = appt_student_data |>
    dplyr::group_by(`Institution Name`) |>
    dplyr::summarise(Appt = sum(Appt)),
  
  var = "Appt"
)
```

  </div>
  
</div>

<div class="row">

```{r appt-student-group-plot, fig.width=8}
appt_student_data |>

  dplyr::group_by(Year) |>
  dplyr::summarise(Mean = mean(Appt, na.rm = TRUE), 
                   Median = median(Appt, na.rm = TRUE),
                   Max = max(Appt, na.rm = TRUE)) |>
  
  tidyr::pivot_longer(
    cols = !Year,
    names_to = "measure",
    values_to = "amount"
  ) |>
  
  mutate(measure = factor(measure, levels = c('Mean','Median','Max'))) |>
  
  ggplot2::ggplot(ggplot2::aes(Year, amount, fill = measure))+
  ggplot2::geom_hline(yintercept = c(0,500,1000,1500,2000), colour = "grey")+
  ggplot2::geom_bar(ggplot2::aes(fill = measure),
                    position = "dodge",
                    stat = "identity") +
  geom_text(aes(label = round(amount,0)),
            colour = "white", size = 8, angle = 90,
            hjust = 1.25, position = position_dodge(.9)
            )+
  annotate("text",
           x = 0.7,
           y = 1750,
           label = "b)",
           size = 15,
           family = params$plotfont)+
  ggplot2::labs(
    y = "Total",
    x = NULL)+
  ggplot2::scale_fill_manual(
    values=c(Mean = "#6AD4BF",
             Median = "#F7BF66",
             Max = "#76828E"))+
  ggplot2::theme(
    text = ggplot2::element_text(size = 45, 
                                 family = params$plotfont),
    axis.text.x = ggplot2::element_text(size = 30, colour = "black"),
    axis.ticks = ggplot2::element_blank(),
    panel.background = ggplot2::element_blank(),
    legend.title = ggplot2::element_blank(),
    legend.text = ggplot2::element_text(size = 30, colour = "black"),
    legend.position = "right"
  )
```
  
</div>

### Professional Staff Appointments + Email Consultations (Alumi only)

<div class="row">

  <div class="col-sm-7">

```{r appt-alum-plot}
appt_alum_data |>
  
  mutate(dim2 = factor(dim2, levels = c('Email Consultations','Appointments*'))) |>
  
  ggplot2::ggplot(ggplot2::aes(reorder(`Institution Name`, engage), engage))+
  ggplot2::geom_hline(yintercept = c(0,500,1000,1500), colour = "grey")+
  ggplot2::geom_bar(ggplot2::aes(fill = dim2),
                    position = "stack",
                    stat = "identity")+
  ggplot2::labs(
    y = "Total",
    x = NULL,
    caption = "*In-Person, Phone, or Video Chat"
  )+
  ggplot2::scale_fill_manual(
    values = c(
      `Email Consultations` = "#6AD4BF",
      `Appointments*` = "#F7BF66"
    )
  )+
  ggplot2::theme(
    text = ggplot2::element_text(size = 40, family = params$plotfont),
    axis.text.x = ggplot2::element_blank(),
    axis.ticks = ggplot2::element_blank(),
    panel.background = ggplot2::element_blank(),
    legend.title = ggplot2::element_blank(),
    legend.position = "top"
  )
```

  </div>
  
  <div class="col-sm-5">

```{r appt-alum-table}
tableViz(
  data = appt_alum_data |>
    dplyr::group_by(`Institution Name`) |>
    dplyr::summarise(engage = sum(engage)),
  
  var = "engage", 
  na.rm = TRUE
  )
```

  </div>
  
</div>

### Professional Staff Appointments + Email Consultations per Total FTE

<div class="row">

  <div class="col-sm-7">

```{r appt-fte-plot}
appt_fte_data |>
  ggplot2::ggplot(ggplot2::aes(reorder(`Institution Name`,ratio),ratio))+
  ggplot2::geom_hline(yintercept = c(0,200,400,600,800), colour = "grey")+
  ggplot2::geom_bar(stat = "identity", fill = "#7CBCE8")+
  
  ggplot2::labs(
    x = NULL,
    y = "Appt. to FTE Ratio",
    caption = "Note: includes only institutions that\n reported both appointments and FTE"
  )+
  
  ggplot2::theme(
    text = ggplot2::element_text(size = 40, family = params$plotfont,
                                 lineheight = .5),
    plot.caption = element_text(size = 25),
    panel.background = ggplot2::element_blank(),
    axis.ticks = ggplot2::element_blank(),
    axis.text.x = ggplot2::element_blank()
  )
```

  </div>
  
  <div class="col-sm-5">

```{r appt-fte-table}
tableViz(appt_fte_data, var = "ratio", na.rm = TRUE)
```
  </div>
  
</div>

### Student Engagement by Class Year

<div class="row">

  <div class="col-sm-7">

```{r sengage-year-plot}

sengage_year_data |>
  
  dplyr::group_by(dim1) |>
  dplyr::summarise(Mean = mean(engage, na.rm = TRUE), 
                   Median = median(engage, na.rm = TRUE),
                   Max = max(engage, na.rm = TRUE)) |>
  dplyr::mutate(dim1 = stringr::str_replace(dim1, regex("TOTAL"),"Total\n")) |>
  tidyr::pivot_longer(
    cols = !dim1,
    names_to = "measure",
    values_to = "engage"
  ) |>
  
  dplyr::mutate(dim1 = factor(dim1, levels = c(
    "First-Year",
    "Sophomore",
    "Junior",
    "Senior",
    "Total\n (all classes)"))
  ) |>
  
  mutate(measure = factor(measure, levels = c("Mean","Median","Max"))) |>
  
  ggplot2::ggplot(ggplot2::aes(dim1, engage, fill = measure))+
  
  ggplot2::geom_hline(yintercept = c(0,25,50,75,100), colour = "grey")+
  ggplot2::geom_bar(ggplot2::aes(fill = measure),
                    position = "dodge",
                    stat = "identity")+
  geom_text(aes(label = round(engage,0)),
    colour = "white", size = 9,
    vjust = 1.25, position = position_dodge(.9)
    )+
  
  ggplot2::scale_y_continuous(limits = c(0,100), breaks = c(0,25,50,75,100))+
  ggplot2::labs(
    y = "Engagement (%)",
    x = NULL
  )+
  ggplot2::scale_fill_manual(
    values=c(Mean = "#6AD4BF",
             Median = "#F7BF66",
             Max = "#76828E"
             #, `Your School` = "#217DBB"
             )
    )+
  ggplot2::theme(
    text = ggplot2::element_text(size = 45, family = params$plotfont),
    axis.ticks = ggplot2::element_blank(),
    axis.text.x = ggplot2::element_text(size = 30, lineheight = 0.5, colour = "black"),
    panel.background = ggplot2::element_blank(),
    legend.title = ggplot2::element_blank(),
    legend.position = "top"
    )
```

  </div>
  
  <div class="col-sm-5">
  
`r nTab(question_list$Q21$Q21_5_4)`

\n \n Note: Engagement \n includes appointments \n w/ professional staff \n and peer advisors and \n programs and events

  </div>
  
</div>

### Student Engagement by Type of Engagement

<div class="row">

  <div class="col-sm-7">

```{r sengage-type-plot}
sengage_type_data |>

  dplyr::select(!c(main:sub2,Question,dim1))  |>
  dplyr::mutate(across(`Undergraduate enrollment`:engage, as.numeric)) |>
  
  dplyr::group_by(dim2) |>
  dplyr::summarise(Mean = mean(engage, na.rm = TRUE), 
                   Median = median(engage, na.rm = TRUE),
                   Max = max(engage, na.rm = TRUE),
                   #`Your School` = mean(engage[`Institution Name`== params$college], na.rm = TRUE)
  ) |>
  tidyr::pivot_longer(
    cols = !dim2,
    names_to = "measure",
    values_to = "engage"
  ) |>
  
  mutate(measure = factor(measure, levels = c('Mean','Median','Max'))) |>
  
  ggplot2::ggplot(ggplot2::aes(dim2,engage, fill = measure))+
  
  ggplot2::geom_hline(yintercept = c(0,25,50,75,100), colour = "grey")+
  ggplot2::geom_bar(ggplot2::aes(fill = measure),
                    position = "dodge",
                    stat = "identity")+
  geom_text(aes(label = round(engage,0)),
            colour = "white", size = 9,
            vjust = 1.25, position = position_dodge(.9)
            )+
  ggplot2::scale_y_continuous(limits = c(0,100), breaks = c(0,25,50,75,100))+
  scale_x_discrete(labels = function(x) stringr::str_wrap(x, width = 15))+
  ggplot2::labs(
    y = "Engagement (%)",
    x = NULL
  )+
  ggplot2::scale_fill_manual(
    values=c(Mean = "#6AD4BF",
             Median = "#F7BF66",
             Max = "#76828E"
             #, `Your School` = "#217DBB"
    )
  )+
  ggplot2::theme(
    text = ggplot2::element_text(size = 45, family = params$plotfont,
                                 lineheight = .5),
    axis.ticks = ggplot2::element_blank(),
    axis.text.x = ggplot2::element_text(size = 30, colour = "black"),
    panel.background = ggplot2::element_blank(),
    legend.title = ggplot2::element_blank(),
    legend.position = "top"
  )
```

  </div>
  
  <div class="col-sm-5">

```{r sengage-type-table}
sengage_type_data |>
  
  mutate(engage = as.numeric(engage)) |>
  
  group_by(`Institution Name`) |>
  summarise(engage = mean(engage, na.rm = TRUE)) |>
  
  dplyr::filter(is.finite(engage)) |>
  
  tableViz(var = 'engage', subtitle = "School Averages")
```

  </div>
  
</div>


### Experiential Learning Participation'

*% of students who completed by graduation*

<div class="row">

  <div class="col-sm-9">

```{r exper-learning-plot}
exper_learning_data |>
  
  dplyr::mutate(dim1 = stringr::str_replace(dim1,
                                           "Internship.+research\\)",
                                           "Internship**")) |>
  dplyr::group_by(dim1) |>
  dplyr::summarise(Mean = mean(exper, na.rm = TRUE), 
                   Median = median(exper, na.rm = TRUE),
                   Max = max(exper, na.rm = TRUE)
                   #, `Your School` = mean(exper[`Institution Name`==params$college])
  ) |>
  
  tidyr::pivot_longer(
    cols = !dim1,
    names_to = "measure",
    values_to = "exper"
  ) |>
  
  mutate(measure = factor(measure, levels = c('Mean','Median','Max'))) |>
  
  ggplot2::ggplot(ggplot2::aes(reorder(dim1,-exper),exper, fill = measure))+
  
  ggplot2::geom_hline(yintercept = c(0,25,50,75,100), colour = "grey")+
  ggplot2::geom_bar(ggplot2::aes(fill = measure),
                    stat = "identity",
                    position = "dodge")+
   geom_text(
    aes(label = round(exper,0)),
    colour = "white", size = 9,
    vjust = 1.5, position = position_dodge(.9)
    )+
  ggplot2::scale_x_discrete(
    labels = function(x) stringr::str_wrap(x, width = 12)
    )+
  ggplot2::labs(
    x = NULL,
    y = "% of Students",
    caption = "*Internship, pre-licensure field experience, mentored experience or similar professional experience\n **Including pre-licensure field experience, NOT including mentored undergraduate research"
  )+
  ggplot2::scale_fill_manual(
    values=c(Mean = "#6AD4BF",
             Median = "#F7BF66",
             Max = "#76828E"
             #, `Your School` = "#217DBB"
    )
  )+
  ggplot2::theme(
    plot.caption = ggplot2::element_text(size = 20, 
                                         margin = ggplot2::margin(t = "10")),
    text = ggplot2::element_text(size = 45, family = params$plotfont,
                                 lineheight = .5),
    axis.text.x = ggplot2::element_text(size = 25, colour = "black"),
    panel.background = ggplot2::element_blank(),
    axis.ticks = ggplot2::element_blank(),
    legend.position = "top",
    legend.title = ggplot2::element_blank()
  )

```

  </div>
  
  <div class="col-sm-3">

```{r exper-learning-table, echo=FALSE}

exper_learning_data |>
  filter(!is.na(exper)) |>
  group_by(dim1)|>
  summarise(count = n()) |>
  
  mutate(dim1 = stringr::str_remove_all(dim1,"\\(.+\\)"),
         dim1= stringr::str_remove_all(dim1, "\\*"))|>
  gt::gt() |>
  
    
  gt::tab_header(title = "Summary",
                 subtitle = "# of respondents by experience") |>
  
  
  gt::cols_label(dim1 = "Experience",
                 count = "N")|>
  
  gt::tab_style(
      style = list(
        gt::cell_text(weight = "bold")
      ),
      locations = gt::cells_column_labels(
        columns = everything()
      )
    ) |>
  gt::tab_style(
      style = list(
        gt::cell_text(style = "italic")
      ),
      locations = gt::cells_title(groups = "subtitle")
    ) |>
gt::cols_width(
      dim1 ~ px(250)
    )

```

  </div>
  
</div>

<hr/>

## Budget

### Total Available Funding

*Operating + Endowed Funds + Expendable Gifts + Other*

<div class="row">

  <div class="col-sm-7">
  
  What do we do about Amherst? 7936792 isn't obviously wrong.
```{r total-funding}
total_budget |>
  
  mutate(Budget = factor(Budget, levels = c('Total_OP','Total_NOP'))) |>
  
  ggplot(aes(reorder(`Institution Name`,amount_mil), amount_mil, fill = Budget))+
  geom_hline(yintercept = seq(0,10,by=5), colour = "grey")+
  geom_bar(stat = 'identity')+
  labs(
    x = NULL,
    y = "Total (in millions)",
    fill = "Budget Type"
  )+
  scale_fill_manual(values=c("#F7BF66","#6AD4BF"),
                    breaks=c("Total_OP", "Total_NOP"),
                    labels=c("Operating", "Non-Operating"))+
  scale_y_continuous(breaks = seq(0,10,by=5),
                     labels = c("0","5","$10"))+
  theme(
    text = element_text(family = params$plotfont, size = 40),
    panel.background = element_blank(),
    axis.ticks = element_blank(),
    axis.text.x = element_blank(),
    legend.text = element_text(size = 25)
  )

```

  </div>
  
  <div class="col-sm-5">

```{r total-funding-table}

tableViz(
  data = total_budget |>
    dplyr::group_by(`Institution Name`) |>
    dplyr::summarise(total = sum(amount)),
  
  var = 'total'
)

```

  </div>
  
</div>

### Endowed Funds

<div class="row">

  <div class="col-sm-7">

```{r endow-fund-plot}
endow_exp_data |>
  ggplot2::ggplot(ggplot2::aes(reorder(`Institution Name`, amount_mil), amount_mil))+
  ggplot2::geom_hline(yintercept = c(0,0.5,1,1.5,2), colour = "grey")+
  ggplot2::geom_bar(stat = "identity", fill = "#7CBCE8") +
  ggplot2::labs(
    y = "Total (in millions)",
    x = NULL
  )+
  
  ggplot2::scale_y_continuous(labels = c("0","0.5","1","1.5","$2"))+
  
  ggplot2::theme(
    text = ggplot2::element_text(family = params$plotfont, size = 40),
    panel.background = ggplot2::element_blank(),
    axis.text.x = ggplot2::element_blank(),
    axis.ticks = ggplot2::element_blank(),
    legend.title = ggplot2::element_blank(),
    legend.text = ggplot2::element_text(size = 30)
  )
```

  </div>
  
  <div class="col-sm-5">

```{r endow-fund-table}
tableViz(data = endow_exp_data |>
           dplyr::group_by(`Institution Name`) |>
           dplyr::summarise(amount = sum(amount)), 
         
         var = 'amount')
```

  </div>
  
</div>

### Expendable Gifts

<div class="row">

  <div class="col-sm-7">

```{r expend-gift-plot}
gift_data |>
  ggplot2::ggplot(ggplot2::aes(reorder(`Institution Name`, amount_mil), amount_mil))+
  ggplot2::geom_hline(yintercept = c(0,0.5,1,1.5), colour = "grey")+
  ggplot2::geom_bar(stat = "identity", fill = "#7CBCE8")+
  ggplot2::labs(
    y = "Total (in millions)",
    x = NULL
  )+
  
  ggplot2::scale_y_continuous(breaks = c(0,0.5,1,1.5),
                              labels = c("0","0.5","1","$1.5"))+
  
  ggplot2::theme(
    text = ggplot2::element_text(family = params$plotfont, size = 40),
    panel.background = ggplot2::element_blank(),
    axis.text.x = ggplot2::element_blank(),
    axis.ticks = ggplot2::element_blank(),
    legend.title = ggplot2::element_blank(),
    legend.text = ggplot2::element_text(size = 30)
  )
```

  </div>
  
  <div class="col-sm-5">

```{r expend-gift-table}
gift_data |>
  dplyr::group_by(`Institution Name`) |>
  dplyr::summarise(amount = sum(amount)) |>
  dplyr::filter(!is.na(amount) & amount > 0) |>
  tableViz(var = "amount")
```

  </div>
  
</div>

<hr/>

Special thanks to **ACKNOWLEDGEMENTS HERE**


